Forecasting U.S. Presidential Election Outcomes: A Poll-Based Predictive Model Using YouGov Data

### 2024-11-03 paper/paper.qmd
Add some contents on Model section.

>>>>

## Model Validation and Diagnostic Checks
We validated the model through out-of-sample testing and calculated Root Mean Squared Error (RMSE) to assess prediction accuracy.These diagnostics confirmed that the model adequately converged. Additionally, alternative models, including a generalized linear model and polynomial terms, were tested, but the Bayesian linear model provided a balance of interpretability and predictive performance.
